\LARGE \bf Object Detection-Based Behaviour using Deep-Learning on Thymio

### 2018-06-04 paper/paper.tex
fixed 1 typo.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
The ability to classify objects in both space and domain is encoded in an enormous variety of species on the planet. Recently, deep learning approaches have been developed to make machines able to mimic the same task with interesting results. With this paper, we propose a minimal architecture to achieve the same goal using a cheap two-wheels robot, the Thymio, with a mounted frontal camera in order to make it moves based on the objects detected in the surrounding. 
\end{abstract}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
The ability to classify objects in both space and domain is encoded in an enormous variety of species on the planet. Recently, deep learning approaches have been developed to make machines able to mimic the same task with interesting results. With this paper, we propose a minimal architecture to achieve the same goal using a cheap two-wheels robot, the Thymio, with a mounted frontal camera in order to move it based on the objects detected in the surrounding. 
\end{abstract}
